systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-25 paper/trunk/systemfit_other.tex
I'm not sure what I changed here.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@644 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Hausman \citep{hausman78} developed a test for misspecification.
The null hypotheses of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is,
\begin{equation}
  m = \left( \hat{\beta}_2 - \hat{\beta}_3 \right)^{'}
      \left( \Cov \left[ \hat{\beta}_2 \right] -
             \Cov \left[ \hat{\beta}_3 \right] \right)
      \left( \hat{\beta}_2 - \hat{\beta}_3 \right)
\label{eq:hausman}
\end{equation}
where $\hat{\beta}_2$ and $\Cov \left[ \hat{\beta}_2 \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\hat{\beta}_3$ and $\Cov \left[ \hat{\beta}_3 \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypotheses this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.

>>>>

\citet{hausman78} developed a test for misspecification.
The null hypotheses of the test is that all exogenous variables are
uncorrelated with all disturbance terms.
Under this hypothesis both the 2SLS and the 3SLS estimator are consistent
but only the 3SLS estimator is (asymptotically) efficient.
Under the alternative hypothesis the 2SLS estimator is consistent
but the 3SLS estimator is inconsistent.
The Hausman test statistic is,
\begin{equation}
  m = \left( \hat{\beta}_{2SLS} - \hat{\beta}_{3SLS} \right)^{'}
      \left( \Cov \left[ \hat{\beta}_{2SLS} \right] -
             \Cov \left[ \hat{\beta}_{3SLS} \right] \right)
      \left( \hat{\beta}_{2SLS} - \hat{\beta}_{3SLS} \right)
\label{eq:hausman}
\end{equation}
where $\hat{\beta}_{2SLS}$ and $\Cov \left[ \hat{\beta}_{2SLS} \right]$ are the estimated
coefficient and covariance matrix from 2SLS estimation, and
$\hat{\beta}_{3SLS}$ and $\Cov \left[ \hat{\beta}_{3SLS} \right]$ are the estimated
coefficients and covariance matrix from 3SLS estimation.
Under the null hypotheses this test statistic has a
$\chi^2$ distribution with degrees of freedom equal to the number of
estimated parameters.
